\documentclass{article}

\title{Story}
\author{Angelyna Ye}

\begin{document}
\maketitle

\section{"For thousands of years, I have stayed inside secretly, watching different periods of people, coming by and walking away. I am always waiting for you to come. Nobody has ever known and seen me until now."}

\section{--------------}
\section{Moon is drowsily shining in the sky.} 
%Story Base BEFORE This Line 


\section{It is doomed to be an unpeaceful night. Near the cove, a factious fight is in progress. Beleaguered by hoods, a middle-aged man with only one strange red eye runs away. The man turns into a narrow street, followed by FBI unexpectedly. Blood is dripping, but he keeps sprinting. A devious store stands at the end of the shabby street.  Following the man, the FBI go into the store. The man stops in front of the counter. He bents down on the floor, and crawls three times in a counterclockwise direction. Suddenly, a secret door gradually appears on the wall. A crazy sculpture exhibition is holding behind the door. Sculptures are assembled arbitrarily. Although they range in size, they are all concrete block sculptures. The man walks through the crows without accosting anyone. He keeps walking until he reaches this special sculpture in the right corner of the room. It is an incredibly lifelike carving of a young girl's head, but some bizarre red spots destroy the whole beauty of her alluring face. The sculpture is putted inside a dark red, enormous spoon. Staring at the carving, he soliloquizes. "Why she looks like her? " His voice is shivering.} 
\section{The dim lights keep flickering. A garrulous mercenary can't bear them and bursts into expletives:"What the hell is going on! I can't stand the damn lights anymore!"}
\section{"tluck..tlock...tluck..tlock" the sculpture of the young girl is dripping blood, drop by drop. No one noticed. The girl raises sides of her lip. Her smile is sweet and innocent in a bizarre way. } 
\section{The man keeps staring at the sculpture for a moment. Then, he picks out a small doll from the left pocket of his wind coat. He puts it besides the statue, bends down his body, and kisses the carving. As soon as his lip touches the forehead of the sculpture, the light goes out. Everyone is in complete quiet darkness. Someone is singing blithely…}

\section{--------------}
\section{In a scenic town, lived a happy family. There are five people in the family, father, mother, little brother and a little girl. Father is a debonair man; the mother is an affable woman. What felicity this family has. From one day, for an unknown reason, father's one eye becomes red whenever the night comes and he never gets older since then. 
\section{The birds are singing; the flowers are blooming; the sun is shining. What a beautiful day. Today, the father goes out of the town on a fourteen-day-business-trip. Days pass. Nothing strange happen until the thirteen day's midnight. It is a peaceful night. Suddenly, a scream breaks the peace of night. The brother and the little girl are sleeping under the bed. The little girl awakes. She can't see anything except a red eye and the cold light of the blade. It stares maliciously at the bed.  Blood is splashing; blood is pouring … }
 \section{Waking up, the little girl finds his father back home with an alluring woman and a small boy who is always holding a cute doll in his hands. Surprisedly, the room is clean and tidy, just like it used to be. Blood has disappeared with the mother. No one knows where they go. Something strange happens. Whenever the little girl asks others about her mother, everyone claims that she has already disappeared for years. Everything is normal again, except there are six people in the family now. }

\section{--------------}
\section{The alluring woman becomes the step-mother, and the boy with a cute doll becomes their little brother. Whenever the father is home, the step-mother treats the kids friendly.  However, whenever the father is away, she makes two kids do every housework and beats them for fun.  But who believes such an affable woman will do those offensive things to these cute kids.}

\section{They grow up day by day. The brother gradually dares to revolt against her step-mother, who holds the grudge. Finally, one day, when they are quarreling again in the kitchen, the step-mother picks up the chef knife and hacks at the brother. She chops and chops, with a big satisfied smile. The step-mother enjoys so much that she doesn't notice, in the corner of the kitchen, hide the little girl. Fearful to death, the little girl can't even say a word. Again and again, mother chops crazily and laughs excitedly.  Not until a century passes, does the mother stop. Piece by piece, the mother assembles the body of the brother and cooks them.}

\section{The smell of the delicious meat is spreading all over the house while father comes back. The father gobbles up the meat and drinks up the soup. " Mmm, yummy, why today's meat is so fresh and tasty?" Father licks his lips.}
\section{"Because they are from a young creature." answered mother.}
\section{"Where is my little boy?" asked the father.}
\section{"Oh, he went to his friends' home. Uhhh... The grown-up boy loves friends better than their old parents." the complained.} 
\section{Everyone on the table is drinking and eating with joy, except the little girl. She sits there sadly. "What's going on, my honey? Are you okay? " the mother asks. }
\section{"I'm I'm okay. I just don't feel myself today." the little girl replied with fear.} 
\section{"Go have some rest! Your face is so pale."}
\section{The little girl picks up few bones from the bawl and sneaks out of the house without saying a word. She wanders in the forest. She is so sad that she doesn't even notice her mother is following her closely. The little girl stops in front of a bush of red roses and buries the bones under the beautiful flowers. Her mother is tiptoeing towards her. The little girl turns back, but all is too later. The little girl's head rolls towards the roses. Without any remorse, mother bursts into laughs again.} 
\section{Back home, mother lies to the father again}
\section{When the father is away, the mother pours gypsum down the girl's face, cautiously flays off the skin and sews around a doll. Two masterpieces have been created.}
\section{The father finally finds out that mother is the witch who turns his eye red and helps him expand his lifespan as he has asked. But, all is too late. He keeps querying others about his two kids, but no one knows.}
\section{Now there are only two people in the family.}
\section{--------------}
\section{"Papa killed mama, but no one knows. Blood is dripping; blood is dropping. That's great!"
"Mama chopped him. Papa ate him. Mmm, yummy!"}
\section{"Mama flayed me. Mama chopped me.  She sewed a doll with my skin. She made a statue with my head. All are too great! "}
\section{On and on, the young voice lingers in the room. Step by step, all people inside the store froze and became sculptures. Aha, now, the store is full of masterpieces.} 
\section"Still, no one knows me. All my friends are on the shelves of my little sculpture store. They are having such a great time. Would you like to join?"}
\end{document}
